MSDS 7333 Case Study 06

### 2017-06-18 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Added rest of Matt's work to markdown

>>>>

<font color = "red">(Continued from baldree-case6.r)</font>

> for k-NN, we will include training data with angles close to point in question since angle matters.
> if we want one angle, then include angles that match the rounded orientation of new observation.
> if we want two angles, then pick two multiples of 45 degrees that flank the new observation's orientation.
> if we want three angles, then pick the closest 45 degree increment and on either side of it.
> what if we didn't want to collapse the signal strengths across the m angles, and
> instead return a set of mx166 signals for each access point?

```{r}
for (ap in c("", rejectedAP, chosenAP)){
  test = onlineSummary[, !(names(onlineSummary) %in% ap)]
  train = subset(offlineSummary, mac != ap)
  err = predictionErrors(test, train, numberOfAnglers = 1, k = 3)
  print(paste(ap, err))
}
```

```{r}
#Iterate through 1 to 3 neighbors with 1 to 3 angles for each scenario to determine best combination
#for cross validation
for (ap in c("None", rejectedAP, chosenAP)){
  if (ap == "None"){
    test = onlineSummary
    train = offlineSummary
  } else {
    test = onlineSummary[, !(names(onlineSummary) %in% ap)]
  }

  estXY = predXY(newSignals = test[, 6:11],
                 newAngles = test[, 4],
                 train, 
                 numAngles = 3, k = 3)
  actXY = test[, c("posX", "posY")]
  err = calcError(estXY, actXY)

  print(paste(ap, err))
}
```

<font color = "green" size = "5px"><b>This is where we will perform cross validation and plot for desired AP for a range of k's </b></font>
